---
title: "In-Class Activity:  Working with strings"
author: "Benjamin Fales"
date: "01/31/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Setup


```{r}

library(tidyverse)
library(lubridate)
library(rebus)

message <- read.csv("https://www.dropbox.com/s/lgpn3vmksk3ssdo/scrambled_message.txt?dl=1", stringsAsFactors = FALSE)$Word
```


## Warm-up exercises

1. How many characters are in the scrambled message?
There are 2544 characters in the scrambled message.
```{r}

length <- sum(str_length(message))

length
```

2. How many of these characters are white space?
1652 characters are white space.
```{r}
whitespace <- sum(str_count(message, " "))

whitespace    

```

3. How many words are in the scrambled message?
There are 127 words in the message.
```{r}
words <-  sum(str_detect(message, pattern = (".")))

words
```

4. Show all the punctuation marks in the scrambled message.
```{r}
punctuation <- message %>%  
  str_extract_all(pattern = ("[:punct:]")) %>% 
  unlist()

punctuation
```

5. Print out, in all capitals, the longest word in the scrambled message.
```{r}
longest <- str_to_upper(message[which.max(str_length(message))])

longest
```


6. Print out every word that starts with the letter "m" and ends with the letter "z" in the scrambled message.
```{r}
message %>% 
  str_extract_all(pattern = "m.*z") %>% 
  unlist()
```

## Decode a message

Now complete the following steps to decode the message:

1. Remove any spaces before or after each word.
```{r}
message <- message %>%  
  str_replace_all(" ", "")
```

2. No word should be longer than 16 characters. Drop all extra characters off the end of each word.
```{r}
message <- message %>%  
  str_trunc(16, ellipsis = "")
```

3. Any time you see the word "ugh", with any number of h's, followed by a punctuation mark, delete this.
```{r}
message2 <- message %>%
  str_replace_all(pattern = ("ugh+[:punct:]"), "")
```


4. Replace all instances of exactly 2 a's with exactly 2 e's.
```{r}
message3 <- message2 %>% 
  str_replace_all("aa", "ee")
```

5. Replace all z's with t's.
```{r}
message4 <- message3 %>% 
  str_replace_all("z","t")
```

6. Every word that ends in b, change that to a y.  *Hint: punctuation!*
```{r}
message5 <- message4 %>% 
  str_replace_all("b[:punct:]*$", "y")
```

7. Every word that starts with k, change that to a v.  *Hint: capitalization!*
```{r}
message6 <- message5 %>% 
  str_replace_all("^k", "v") %>% 
  str_replace_all("^K", "V")
```

8. Use `str_c` to recombine all your words into a message.
```{r}
message7 <- message6 %>% 
  str(c,  sep = " ", collapse = "")
```

9. Find the movie this quote is from, and enter that on PolyLearn.
