---
title: 'Lab 3: Billboard Top 100'
author: "Benjamin Fales"
date: "2/3/2019"
output: html_document
---
```{r}
library(tidyverse)
library(lubridate)
songs <- read.table("https://www.dropbox.com/s/jrwjthqo9b5o07g/billboard_songs.txt?dl=1",header = TRUE,stringsAsFactors = FALSE)
```

```{r}
songs1 <-
songs %>% mutate(
  end_date = ymd(chart.date),
  start_date = end_date - weeks(weeks.on.chart)
)
```


1. What 10 songs spent the longest on the charts? Give only the title, artist, and weeks.
```{r}
weeksonchart <-
  songs1 %>% 
  arrange(desc(weeks.on.chart)) %>% 
  select(title, artist, weeks.on.chart) %>% 
  top_n(10, weeks.on.chart)

weeksonchart
```

2. What date did the oldest song(s) in this dataset leave the charts? Give only the date.
```{r}
old_song <- 
  songs1 %>%
  arrange(start_date) %>% 
  select(end_date)

old_song[1,]
```

3. What songs could have been played at your 16th birthday party? That is, which songs overall.peaked at #1 and entered the charts within a couple months (before or after) your 16th birthday? Give only the song title, artist, and date of chart entry
```{r}
birthday <- as.Date("1997-07-18")
birthday_16 <- birthday + years(16)

bdayparty_16 <- songs1 %>% 
  filter(overall.peak ==1, start_date <= birthday_16 + months(2), end_date >= birthday_16 - months(2)) %>% 
  select(title, artist, start_date)

bdayparty_16
```

4. What is the most common word, at least 4 letters long, used in the title of any song? Give only the
word itself, and its count.
```{r}
titles <- songs1 %>%
  pull(title)
four_char_words <-
  titles %>%
  unlist() %>% 
  str_extract_all(pattern = fixed("[^:alpha:]{4,}"))  
  

four_char_words %>%
table() %>%
sort() %>%
rev() %>%
head(1)
```

5. 5) Which five artists were the most successful in terms of:
• Number of songs that were #1 hits
• Total weeks any of their songs spent on the chart.
```{r}

numberones <-
songs1 %>% 
  filter(overall.peak == 1) %>% 
  group_by(artist) %>%
  summarize_at(vars(title),  funs(n())) %>% 
  arrange(desc(title)) %>% 
  top_n(5)

numberones

weeks_spent <-
  songs1 %>% 
  group_by(artist) %>% 
  summarize_at(vars(weeks.on.chart), funs(sum)) %>% 
  arrange(desc(weeks.on.chart)) %>%
  top_n(5)

weeks_spent
```

