---
title: 'Lab 7: Bootstrapping'
author: "Benjamin Fales"
date: "March 7, 2019"
output: html_document
---

# The Data

```{r data, echo = TRUE, include = FALSE}
library(tidyverse)
library(lubridate)
library(modelr)
library(broom)

salaries <- read.csv("C:/Users/bfale/Desktop/Salaries.csv", header = TRUE, na.strings = c("Not Provided", "Not provided", ""))

options(scipen = 999)
```

### Question 2

The center of the histogram seems to lay around $75,000 of total pay. The histogram as a whole is skewed right. The spread is very large.
```{r Question 2, eval = TRUE, cho = TRUE}

salaries %>% 
  ggplot(aes(x = TotalPay, y = ..density..)) +
  geom_histogram(bins = 50) +
  geom_density()
```

### Question 3
The mean is a fairly reliable measure the typical value of a salary. However, I would use the median as this reflects the large skew to the right that the salary has.
```{r Question 3, echo = TRUE, eval = TRUE}
mean_totalpay <- mean(salaries$TotalPay)

median_totalpay <- median(salaries$TotalPay) 

statistics_salaries <- data.frame(Mean = mean_totalpay, Median = median_totalpay)

statistics_salaries
```

### Question 4
Based on the graph in Question 2, it does not seem reasonable for the normal assumption to be satisfied.

### Question 5
```{r Question 5, echo = TRUE, eval = TRUE }

tidy(t.test(salaries$TotalPay)) %>% 
  select(conf.low, conf.high)
```

#Bootstrapping

### Question 6
Compared to the t dist. confidence interval, they are very similar. The bootstrapped confidence interval is minisculely wider. 
```{r Question 6, echo = TRUE, eval = TRUE}
boots_total <- replicate(1000, sample(salaries$TotalPay, replace = TRUE), simplify = FALSE)

stats_salaries <- map_dbl(boots_total, mean)

conf_salaries <- quantile(stats_salaries, c(0.025, 0.975))

conf_salaries
```

### Question 7
```{r Question 7, echo = TRUE}

midhinge_salaries <- function(dist){
  q1 = quantile(dist,.25)
  q3 = quantile(dist, .75)
  midhinge = (q1 + q3) / 2
  return(midhinge)
}

trim_salaries <- function(dist, trimmed){
  trimmed_mean = mean(dist, trim = trimmed)
  return(trimmed_mean)
}


```

### Question 8
```{r Question 8, echo = TRUE, eval = TRUE}
stats <- data.frame(midhinge = map_dbl(boots_total, midhinge_salaries),
                    median = map_dbl(boots_total, ~quantile(.x, .5)))

stats %>% 
  gather(key = "Stat", value = "Value") %>% 
 ggplot(aes(x = Value, fill = Stat)) +
    geom_density(alpha = 0.5)

trim_stats <- data.frame(trim_05 = map_dbl(boots_total, ~trim_salaries(.x, .05)),
                        trim_10 = map_dbl(boots_total, ~trim_salaries(.x, .10)),
                         trim_25 = map_dbl(boots_total, ~trim_salaries(.x, .25)))

trim_stats %>% 
  gather(key = "Trim_Mean" , value = "Value") %>% 
  ggplot(aes(x = Value, fill = Trim_Mean)) +
  geom_density(alpha = 0.5) 

```

### Question 9
Because of the large skew to the right, as well as the large density of the population that seems to have a salary of 0, it would be reliable to use the 25% trimmed mean. This trims out the lowest salaries as well as the highest salaries.
```{r Question 9, echo = TRUE, eval = TRUE}
data.frame(
  conf_midhinge = quantile(stats$midhinge, c(.25, .75)),
  conf_median = quantile(stats$median, c(.25, .75)),
  conf_trim_05 = quantile(trim_stats$trim_05, c(.25, .75)),
  conf_trim_10 = quantile(trim_stats$trim_10, c(.25, .75)),
  conf_trim_25 = quantile(trim_stats$trim_25, c(.25, .75))
)
```

